Real-space computation of $E$/$B$-mode maps I: Formalism, Compact Kernels, and Polarized Filaments

### 2018-07-31 articles/formalism/sections/real_space_formalism.tex
relocated footnote

We can only measure the total Stokes vector, a sum of the part that corresponds to scalar $E$ and the part that corresponds to $B$.  The $E$/$B$ modes are orthogonal to each other in the sense that their respective operators are orthogonal to each other as discussed in \sec{sec:mat_pol_intro}. It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization. In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar $E/B$ modes. The algebra is more involved, but the derivation is similar to that discussed in \sec{sec:qu2eb}, so we refrain from presenting the detailed calculations here and outline only the key points. We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators. The Stokes parameters corresponding to each scalar mode are given by the following expressions:

>>>>

We can only measure the total Stokes vector, a sum of the part that corresponds to scalar $E$ and the part that corresponds to $B$.  The $E$/$B$ modes are orthogonal to each other in the sense that their respective operators are orthogonal to each other as discussed in \sec{sec:mat_pol_intro}. It is possible to decompose the Stokes vector \vp{} into one \vp{\rm E} that purely contributes to $E$ modes and another \vp{\rm B} that purely contribute to the $B$ modes of polarization. In this section we derive the real space operators which operate on the total Stokes vector and yield this decomposition, without ever having to explicitly evaluate the scalar $E/B$ modes \footnote{While this manuscript was in preparation, work appeared in \cite{2018JCAP...05..059L} that discussed a similar idea of real-space purification of Stokes $Q/U$ parameters to their $E/B$ counterparts, but we treat it here in much more detail.}. The algebra is more involved, but the derivation is similar to that discussed in \sec{sec:qu2eb}, so we refrain from presenting the detailed calculations here and outline only the key points. We use the harmonic space projection operators $\tilde O_{E/B}$, defined in \eq{eq:har_eb_op}, to derive the respective real space operators. The Stokes parameters corresponding to each scalar mode are given by the following expressions:
